A* with perfect potentials

### 2019-10-24 paper/ch_potentials.tex
better keywords
more concrete abstract

\keywords{Route planning, Contraction Hierarchies, A*}%TODO mandatory; please add comma-separated list of keywords

@@

\begin{abstract}
Quickly determining shortest paths in networks is an important ingredient for many routing applications.
While Dijkstra's algorithm can be used to solve these problems, it is too slow for many practical problems.
A* is an extension to Dijkstra's algorithm.
It uses a potential function to estimate the distance of each node to the target.
By adding these estimates to the queue keys, the search is directed towards the target.
The quality of this potential determines the performance of A*.
We introduce a novel way to efficiently calculate potentials through Contraction Hierarchies.
These potentials are perfect with respect to a lower bound graph.
They can be used to speed up shortest path queries for extended problem settings like frequently changing or time-dependent edge weights.
\end{abstract}

>>>>

\keywords{shortest path, road graphs, goal-directed search, contraction hierarchy}%TODO mandatory; please add comma-separated list of keywords

@@

\begin{abstract}
Quickly determining shortest paths in networks is an important ingredient for many routing applications.
While Dijkstra's algorithm can be used to solve these problems, it is too slow for many practical problems.
A* is an extension to Dijkstra's algorithm.
It uses a potential function to estimate the distance of each node to the target.
By adding these estimates to the queue keys, the search is directed towards the target.
The quality of this potential determines the performance of A*.
We introduce a novel way to efficiently calculate perfect potentials for extended problem settings where a lower bound graph is available.
For example, in the case of routing with live traffic, this could be the free flow graph.
\end{abstract}
